This package allows to draw interactive charts from the *JavaScript* library [AmCharts][url_amcharts] using [Hmlwidgets][url_htmlwidgets].
Since it is still in developpment, some functionnalities might have an unexpected behavior. If you encounter the problem, do not hesitate to contact.

---

# Installation

This package is also available on CRAN. However several improvements and bug fixes have been performed since the last submission. The "**dev version**" is preferable. A new submission will be done soon.

Run the following code lines to install **rAmCharts**:

```{r, eval = FALSE}
if (require(devtools)) {
  install.packages("devtools")
} else {}

devtools::install_github("dataKnowledge/rAmCharts")
```

---

## See some examples by runnig `rAmCharts::runShinyExamples()`

---

## New statistical features !

### Histogram: same use as `hist`:
```{r}
library(rAmCharts)
data(iris)
amHist(iris$Sepal.Length, freq = FALSE, breaks = 30, col = "gray")
```

### Boxplot: same use as `boxplot`:

```{r}
library(rAmCharts)
data(iris)
amBoxplot(Sepal.Length~Species, data = iris, col = c("darkblue", "darkred", "lightblue"))
```

[url_amcharts]: http://www.amcharts.com
[url_htmlwidgets]: http://www.htmlwidgets.org
