### Introduction

This package allows the charts from the library [AmCharts][url_amcharts] using
[Hmlwidgets][url_htmlwidgets].

---

### Dependencies

This package requires :

- Main architecture to load js dependencies
```{r, eval = FALSE}
if (!require("htmlwidgets")){
  install.packages('htmlwidgets')
}else{}
```

- Use R functions with pipe for constructing chart
```{r, eval = FALSE}
if (!require("pipeR")){
  install.packages("pipeR")
}else{}
```

- Used in package to manage list
```{r, eval = FALSE}
if (!require("rlist")){
  install.packages("rlist")
}else{}
```

- For the moment, only used in the developpment function...
```{r, eval = FALSE}
if (!require("data.table")){
install.packages("data.table")
}else{}
```

- Use in shiny app:
```{r, eval = FALSE}
if (!require("shiny")){
  install.packages("shiny")  
}else{}
```

Those packages are indicated in the ***DESCRIPTION*** file below the *Depends* tag. Consequently, they are essential.

---

# Installation

Once the above dependent packages available, you can run the following code lines:

```{r, eval = FALSE}
if ( require(devtools) ) {
  install.packages(devtools)
} else{}
devtools::install_github("Djaiff/rAmCharts")
```


---

[url_amcharts]: http://www.amcharts.com
[url_htmlwidgets]: http://www.htmlwidgets.org
