## Warning !

This branch is dedicated to develop the functions am**. Be cautious if you want to use it since we improve or change the code very often. Once they are stable, we will merge them to the master.

---

### Installation

To install the "dev version" (v1.1.3), run the following code lines:

```{r, eval = FALSE}
if (!require(devtools)) {
  install.packages("devtools")
} else {}

devtools::install_github("dataKnowledge/rAmCharts")
```

**NB**:

* Version 1.1.2 is based on [AmCharts][url_amcharts] v3.17.2
* Version 1.1.3 is based on [AmCharts][url_amcharts] v3.18.2

### Known issues

* Problem in Shiny with Firefox (works with Chrome or Safari), the function `renderAmcharts({NULL})` does not clear the chart, use conditionalPanel instead.
* Use in R Markown needs either an url path "http://www.amcharts.com/lib/3" to find images or a local path e.g. `system.file("htmlwidgets/lib", package = "rAmCharts")`. HTML reports also need a call to the method `plot`.

```{r, eval = FALSE}
library(rAmCharts)
data(iris)
pipeR::pipeline(
  amHist(iris$Sepal.Length, freq = FALSE, breaks = 30, col = "gray"),
  setProperties(path = "http://www.amcharts.com/lib/3"),
  # setProperties(path = system.file("htmlwidgets/lib", package = "rAmCharts"))
  plot()
)
```

* Usual R colors work (for instance, light or dark prefixes), however the 'export' feature needs valid CSS colors. To be sure, prefer HTML for exporting option.

[url_amcharts]: http://www.amcharts.com
[url_htmlwidgets]: http://www.htmlwidgets.org
[path_histogram]: ./img/histogram.png
[path_boxplot]: ./img/boxplot.png
