## Version 1.1.3 (based on [AmCharts][url_amcharts] 3.17.3)
___

This package allows to draw interactive charts from the *JavaScript* library [AmCharts][url_amcharts] using [Hmlwidgets][url_htmlwidgets].
Since it is still in developpment, some functionnalities might have an unexpected behavior. If you encounter the problem, do not hesitate to contact.

---

## Installation

This package is also available on CRAN. However several improvements and bug fixes have been performed since the last submission. The "**dev version**" is preferable. A new submission will be done soon.

Run the following code lines to install **rAmCharts**:

```{r, eval = FALSE}
if (!require(devtools)) {
  install.packages("devtools")
} else {}

devtools::install_github("dataKnowledge/rAmCharts")
```

---

### See some examples by runnig `rAmCharts::runShinyExamples()`

---

### Statistical features

#### Histogram:

```{r, eval = FALSE}
library(rAmCharts)
data(iris)
amHist(iris$Sepal.Length, freq = FALSE, breaks = 30, col = "gray")
```
![histogram][path_histogram]


#### Boxplot:

```{r, eval = FALSE}
library(rAmCharts)
data(iris)
amBoxplot(Sepal.Length~Species, data = iris, col = c("blue", "red", "yellow"))
```
![boxplot][path_boxplot]

### Known issues

* Use in R Markown needs either an url path "http://www.amcharts.com/lib/3" to find images or a local path e.g. `system.file("htmlwidgets/lib", package = "rAmCharts")`. HTML reports also need a call to the method `plot`.

```{r, eval = FALSE}
library(rAmCharts)
data(iris)
pipeR::pipeline(
  amHist(iris$Sepal.Length, freq = FALSE, breaks = 30, col = "gray"),
  setProperties(path = "http://www.amcharts.com/lib/3"),
  # setProperties(path = system.file("htmlwidgets/lib", package = "rAmCharts"))
  plot()
)
```

* Usual R colors work (for instance, light or dark prefixes), however the 'export' feature needs valid CSS colors. To be sure, prefer HTML for exporting option.

[url_amcharts]: http://www.amcharts.com
[url_htmlwidgets]: http://www.htmlwidgets.org
[path_histogram]: ./img/histogram.png
[path_boxplot]: ./img/boxplot.png
