---
title: "README"
author: "Jeffery"
date: "29 juin 2015"
output: html_document
---

### Introduction

This package allows the charts from the library [AmCharts][url_amcharts] using
[Hmlwidgets][url_htmlwidgets].

---

# Installation

If necessary install the *devtools* package

```{r, eval = FALSE}
if ( require(devtools) ) {
  install.packages(devtools)
} else{}
```

Once the above package loaded,
`devtools::install_github("Djaiff/rAmCharts")`

---

### Dependencies

The package require some other functionnal packages:

- Main architecture to load js dependencies
```{r, eval = FALSE}
if (!require("htmlwidgets")){
  install.packages('htmlwidgets')
}else{}
```

- Use R functions with pipe for constructing chart
```{r, eval = FALSE}
if (!require("pipeR")){
  install.packages("pipeR")
}else{}
```

- Used in package to manage list
```{r, eval = FALSE}
if (!require("rlist")){
  install.packages("rlist")
}else{}
```

- For the moment, only used in the developpment function...
```{r, eval = FALSE}
if (!require("data.table")){
install.packages("data.table")
}else{}
```

Use in shiny app:
```{r, eval = FALSE}
if (!require("shiny")){
  install.packages("shiny")  
}else{}
```

Those packages are indicated in the ***DESCRIPTION*** file below the *Depends* tag

[url_amcharts]: http://www.amcharts.com
[url_htmlwidgets]: http://www.htmlwidgets.org
